Factors affecting health sector expenditure in OECD countries

### 2025-05-02 code/analysis-code/statistical-analysis.qmd
intro #1
finalizing

Then we will import the dataset

@@

We will now pick the most useful variables from the large pool of 1400+ variables in our dataset, and we will then categorize these variables based on the aspects they cover. For example, if there is avariable named "Annual GDP growth", we will categorize it as an "Economic" variable. Similarly, if there is a variable named "Unemployment rate" or "Total population", we will categorize them as "Social" variable.

@@

Now, we will save our regression result is a HTML table so that we can use to present it in our manuscript.

>>>>

Then we will import the dataset.

@@

We will now pick the most useful variables from the large pool of 1400+ variables in our dataset, and we will then categorize these variables based on the aspects they cover. For example, if there is avariable named "Annual GDP growth", we will categorize it as an "Economic" variable. Similarly, if there is a variable named "Unemployment rate" or "Total population", we will categorize them as "Social" variable. This will help us look into the data more easily

@@

Now, we will save our regression result is a HTML table so that we can use to present it in our manuscript or our supplementary material.

### 2025-05-02 products/manuscript/Manuscript.qmd
finalizing

where $e_{it}$ is the error term. $X_{itk}$ is the $k^{th}$ independent variable ( k= 1 to 5, in the above equation but our research will likely have k>5) $y_{it}$ is the dependent variable, $b_0$ is the intercept, and $b_k$ is the estimated parameter for the $k^{th}$ independent variable.

>>>>

where $e_{it}$ is the error term. $X_{itk}$ is the $k^{th}$ independent variable ( k= 1 to 5 in the above equation but our research will likely have k>5), $y_{it}$ is the dependent variable, $b_0$ is the intercept, and $b_k$ is the estimated parameter for the $k^{th}$ independent variable.
